Autonomous Quadrotor 3D Mapping and Exploration Using Exact Occupancy Probabilities

### 2018-06-09 Conference/IRC 2018/IRC18_final.tex
added Conference folder

@@

%% Prior to TLee edits:
%Robotic mapping is the process of generating maps representing the environment surrounding a robot.
%Mapping serves an important role in tasks such as search-and-rescue, surveillance, and robotic cleaning.
%Several grid-based map representations have been studied, e.g.,~\cite{WolSuk05,MeyBeiBur12,TanThoWolBus14}, because they provide abundant occupancy knowledge about the environment and are computationally tractable. 
%
%Most grid-based mapping representations are designed for 2D, while others are extended to capture a full 3D environment. In particular, occupancy probabilities have been assigned to a uniform 3D grid in~\cite{Andert09,PirRutBisSch11}. Another highly-popular variation of occupancy grid mapping is the Octomap representation~\cite{WurHorBenStaBur10,HorWurBenStaBur13}, which has added features such as extending the mapping limits and changing cell sizes. However, Octomaps, and the 3D uniform grid-based approaches mentioned above, produce cell occupancy probabilities that do not directly depend on the depth sensor stochastic properties. Instead, these approaches determine occupancy probabilities using an approximate function. Another method introduced in~\cite{Thr01,ThrBurFox05} and implemented in 3D with~\cite{SouMaiGon12} uses a simulated learning technique to find these probabilities, which may be difficult over the large dimensional space composed of maps, poses, and measurements. An additional approach such as~\cite{TanThoWolBus14} applies a particle filter to estimate the map. None of these approaches use the sensor properties to directly obtain a Bayesian solution to occupancy probability.
%
%%        1.      sensor fusion in mapping
%The approximate nature of the occupancy probability motivates an exact Bayesian solution that can be applied in 3D. This paper proposes a computationally-efficient algorithm that follows the framework of~\cite{KauLeeAiMos16,KauTakAiLee17} to generate probabilities in a 3D environment. Since this approach only requires the origin and direction of sensor measurements to be known, the algorithm is designed to work for any number of sensors. Sensor fusion from several sources can provide important information about the environment with different levels of sensor certainty, fields of view, and vantage points.
%
%%        2.      proposing a method to combine 3D mapping and 2D exploration: Also, we need to motivate why we are not doing full 3D exploration. Stress that we are proposing a computationally friendly approach to perform 3D mapping with projection using the fact there is less variation in the floor plan along the vertical direction.
%The second topic of this paper deals with autonomous exploration, which provide the policies that govern robotic motion. A common approach is known as frontier-based exploration, proposed for 2D environments in~\cite{Yam97,Yam98} and extended to 3D with~\cite{ZhuDinLinWu15,SenWan16,KleDor13} using the Octomap representation, and similarly in~\cite{SawKriSri09} using a visibility metric. This approach moves robots toward the boarder between certain and uncertain space, though these systematic actions are not based on any consideration of the future probabilistic map uncertainty. Alternatively, there have been exploration techniques that are based on a quantitative measure of uncertainty known as Shannon's entropy~\cite{StaGriBur05}, an uncertainty metric based on grid cell occupancy probabilities. Shannon's entropy is used to acquire expected map information gain in~\cite{KauAiLee16,KauTakAiLee17}, and this paper focusses on extending these concepts to 3D. There are several challenges with obtaining expected information gain of 3D measurement scans, particularly as they relate to computational load. Considering the typically low variation in floor plans that robots explore during indoor explorations, this paper proposes two methods to generate 2D exploration maps that exploit the important characteristics of 3D maps. This process of combining 3D mapping and 2D exploration is completed in a computationally-efficient manner.
%
%%        3.      hardware/software for aerial exploration experiment.
%Finally, this paper comments on the hardware and software necessary to implement these challenging algorithms for an aerial mapping and exploration experiment. This paper provides the basic software structure and features for mapping and generating exploration trajectories on a host computer while running depth sensors and a flight controller onboard a mobile robot.
%
%The paper is organized as follows. The problem is formulated in Section II. Special considerations for mapping and exploration in 3D are established in Section III. A numerical example is demonstrated in Section IV. Experimental results are shown in Section V, followed by conclusions and future work.

@@

% {R ? R3×3 | RT R = I, det R = 1}
Consider a range sensor that provides scans of the surrounding environment in order to identify the closest occupied space. Let the measurement scan at the $t$-th time step be $Z_t$, where $z\in Z_t$ is a single measurement ray. Let the $t$-th pose be denoted by $X_t=\braces{x_t,R_t}$ with location $x_t\in\Re^3$ and attitude $R_t\in\SO=\braces{R\in\Re^{3\times3}|R^\T R=I,\det{R}=1}$, where $X_t$ is assumed to be known. Given the sensor probabilistic properties $p(z|X_t,m)$, commonly referred to as the \emph{forward sensor model}, the goal is finding the \emph{inverse sensor model}, $P(m|z,X_{1:t},Z_{1:t-1})$. To obtain this probability for all cells,~\cite{KauLeeAiMos16,KauTakAiLee17} introduced a reduced map $r\subset m$ composed of $n_r$ cells along $z$, where cells are indexed by increasing distance from $x_t$, and $\mathbf{r}_{k+}$ refers to the event that the $k$-th cell of map $r$ is the closest occupied space. Then, the inverse sensor model for the $k$-th cell is
\begin{align}
\label{eqn:RayISMAnswer}
P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1})&=\eta\tilde P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1}),
\end{align}
where the unnormalized probability of the inverse sensor model is defined as
\begin{align}
\label{eqn:Unnormalized}
\tilde P(\mathbf{r}_{k}|z,X_{1:t},&Z_{1:t-1})\nonumber\\
&=\mathbf{P}_k^-
\bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}\bar{\mathbf{P}}_j^-\bigg\}p(z|\mathbf{r}_{i+},X_t)\mathbf{P}_k^-\bigg]\nonumber\\
&\quad + \bigg\{\prod_{j=0}^{k-1}\bar{\mathbf{P}}_j^-\bigg\}p(z|\mathbf{r}_{k+},X_t)\mathbf{P}_k^-,
\end{align}
where a priori probability is $\mathbf{P}_k^-=P(\mathbf{r}_{k}|X_{1:t-1},Z_{1:t-1})$, its complement is $\bar{\mathbf{P}}_k^-=1-\mathbf{P}_k^-$, $P(\bar{\mathbf{r}}_{0}|X_{1:t-1},Z_{1:t-1})=P(\mathbf{r}_{n_r+1}|X_{1:t-1},Z_{1:t-1})=1$ for convenience, and $p(z|\mathbf{r}_{(n_r+1)+},X_t)$ represents the forward sensor model of a maximum sensor reading. The normalizer $\eta$ is given by
\begin{align}
\label{eqn:allEta}
\eta
&=
\bigg[\sum_{i=1}^{n_{r}+1}\bigg\{\prod_{j=0}^{i-1}\bar{\mathbf{P}}_j^-\bigg\} p(z|\mathbf{r}_{i+},X_t)\mathbf{P}_k^-\bigg]^{-1},
\end{align}
and it is independent of the cell index $k$. Since the terms of \refeqn{Unnormalized} are easily obtained and several are used repeatedly to obtain \refeqn{allEta}, the computational cost of \refeqn{RayISMAnswer} is trivial and can be applied in real-time. This process is repeated for all measurements composing scan $Z_t$.

@@

The inverse sensor model from~\cite{KauLeeAiMos16,KauTakAiLee17} is based on an arbitrary vector spanning 2D space. The distances from the robot to grid cells are obtained geometrically through ray casting. This method is easily extended to 3D space, and the inverse sensor model is applied identically. Since the map is updated ray-by-ray (each measurement ray is considered once by itself), this approach is extended for measurement fusion of any number of sensors; the map is updated by each ray of a scan sequentially, then the map is updated by the rays of the next scan in queue, which might have different characteristics. There are several reasons why a robot might be equipped with multiple sensors, e.g., different fields-of-view or depth sensor properties. The proposed 3D mapping approach can handle measurements from different sources with different properties.

However, implementation in 3D requires several careful considerations. First, the number of cell occupancy probabilities tracked with computer memory increases by a factor of the number of cells in the added dimension. In its current form, the proposed method assumes fixed map limits, so these should be carefully selected with grid cell resolution based on available memory. Second, measurement rays spanning 3D space typically involve more intersections with grid cells. The computational order of ray casting and the inverse sensor model are proportional to the number of grid cells along the ray $n_r$, so careful consideration must be placed on sensor limits and rays per scan that can be considered. Typically, computers small enough to be carried onboard flying robots lack the memory or processing capabilities to update massive maps quickly. Therefore, an onboard computer can simply stream the sensor data, and a more powerful computer can run the mapping.

Additionally, aerial vehicles are frequently subject to fast movements, and the time stamps for pose estimates and depth sensor readings are not guaranteed to align. For example, the most recent pose estimate and measurement scan may have significantly different time stamps while the robot is rapidly rotating. Using these together violates the assumption that the robot pose is well-known for every measurement scan, i.e., $X_t$ and $Z_t$ are given. Therefore, pose estimates and sensor readings must be paired according to their time stamps. A useful tool that easily satisfies this goal is message filtering with the Robot Operating System (ROS), where stamped poses and measurement scans are synchronized using recently received data.

@@

The goal of the proposed autonomous exploration strategy is moving to poses that maximize the information the robot expects to learn about the map, measured with entropy. To achieve this in real-time, careful consideration is placed on computational costs. In particular, the expected entropy computational order of a ray that intersects $n_r$ cells is $(n_r+1)^2$. Since most quadrotor flight is close to hover and floor plans exhibit little variation in the vertical direction, the proposed exploration uses 2D occupancy grid maps located at the desired exploration height. This approach decreases $n_r$ and simplifies the exploration problem with 3D space. These 2D maps project important properties of the 3D map.

@@

Gazebo serves as the simulator node, with plugins to simulate an Asus Xtion color depth sensor and a Hokuyo LIDAR. Gazebo also provides position and attitude transforms from the world to the quadrotor body, and the ability to set robot model states directly.

@@

There are two processes for exploration. The first process is projecting the 3D map onto 2D maps; the same code under different conditional parameters produces two nodes, for collision and entropy maps. The second process subscribes to these two 2D maps; the collision map serves as input for candidate pose consideration and Dijstra's search, and the entropy map is used to predict expected information gain. This node provides path messages, composed of desired poses $0.01$sec apart, that are easily visualized with the ROS visualization package, Rviz.

@@

\begin{figure}[!t]
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_1min.jpg}
        		\caption{$t=1$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_2min.jpg}
        		\caption{$t=2$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_3min.jpg}
        		\caption{$t=3$min}
   	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_4min.jpg}
        		\caption{$t=4$min}
    	\end{subfigure}
	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_5min.jpg}
        		\caption{$t=5$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_6min.jpg}
        		\caption{$t=6$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_7min.jpg}
        		\caption{$t=7$min}
   	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_8min.jpg}
        		\caption{$t=8$min}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Simulated 3D Occupancy Grid Map}
\label{fig:sim3DMap}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.4\textwidth]{entropy_gazebo_aspect3by1.png}
	\caption{Simulated Environment Map Entropy}
	\label{fig:simH}
\end{figure}

@@

\section{Experimental Resutls}

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_north.jpg}
        		\caption{North Region}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_south.jpg}
        		\caption{South Region}
    	\end{subfigure}
	\caption{3D Experimental Environment}
	\label{fig:exp3DEnvironment}
\end{figure}

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.88\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_0min.jpg}
        		\caption{$0$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.88\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_1min.jpg}
        		\caption{$1$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.88\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min.jpg}
        		\caption{$2$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.88\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min47sec.jpg}
        		\caption{$2$min $47$sec (end)}
    	\end{subfigure}
	\caption{3D Occupancy Grid Map and Point Clouds}
	\label{fig:exp3DMap}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.4\textwidth]{entropy_experiment_aspect3by1.png}
	\caption{Experimental Environment Map Entropy}
	\label{fig:expH}
\end{figure}

>>>>

% asdf Author Comments:

%----------------------- REVIEW 1 ---------------------
%PAPER: 45
%TITLE: Autonomous Quadrotor 3D Mapping and Exploration Using Exact Occupancy Probabilities
%AUTHORS: Evan Kaufman, Kuya Takami, Zhuming Ai and Taeyoung Lee
%
%Overall evaluation: 2 (accept)
%
%----------- Overall evaluation -----------
%Paper is well defined and explained. The literature review is also satisfactory. It could be better, if you give further information about how different sensors (Hokuyo, Xtion) fused together to accomplish the mapping task.
%
%
%----------------------- REVIEW 2 ---------------------
%PAPER: 45
%TITLE: Autonomous Quadrotor 3D Mapping and Exploration Using Exact Occupancy Probabilities
%AUTHORS: Evan Kaufman, Kuya Takami, Zhuming Ai and Taeyoung Lee
%
%Overall evaluation: 0 (borderline paper)
%
%----------- Overall evaluation -----------
%In this paper, the authors present a framework for autonomously exploring and mappping an unknown environment from a Quadrotor. The vehicle exploits an inverse sensor model for assigning a probability (that the cell has been explored) to each cell of the map. It also considers both the entropy information of the map and the collision probabilities when computing the next optimal exploration pose.
%
%The paper is overall undestandable, but  some technical sections: 2.a, 2.b, 3.b, 3.c are not easily readable. Providing some explanations to the formule would help the reader to the interpretation.
%
%Some other comments:
%1) Passing from a full 3D map to an "augmented" 2D map is an interesting and smart trick for reducing the computational cost. In spite of this: "Typically,
%computers small enough to be carried onboard flying robots
%lack the memory or processing capabilities to update massive
%maps quickly. Therefore, an onboard computer can simply
%stream the sensor data, and a more powerful computer can
%run the mapping."  The authors should provide some references or giving more details. The computational time depends on several variables, and this seems to be a simplistic motivation for explaining the presence of a ground station for the map management.
%
%2) The ROS message filtering tool just provides in the same callback the temporally closer measurements, but it does not solve the synchronization problem. The authors probably need some interpolation method or something similar. Please explain.
%
%3) "Since most quadrotor flight is close to hover and floor plans
%exhibit little variation in the vertical direction, the proposed
%exploration uses 2D occupancy grid maps located at the
%desired exploration height." Same as (1). It depends on the context. Just by using this assumption, the proposed approach can work in some controlled scenarios with controlled quadrotor motion.
%
%4) The authors basically exploit the two map-based approach in simulation, while the composed map approach in the real environment. Probably testing both approaches in both scenarios would be more interesting. For instance: does the two-map based approach lead to the same slow convergence also in the real case?
%
%5) Main Issue: Following the problem formulation, the inverse sensor model exploits the uncertainties coming from the sensor measurements Z and from the current poses of the robot X. In Simulation, the authors just use the pose provided by the Gazebo Ground truth, while in the real environment the authors rely upon a Vicon, which provides the pose with very little uncertainty. In both cases, it seems that the authors do not introduce any noise or uncertainty in X. In this way, the experimental section cannot prove entirely the effectiveness of the proposed approach, and the reader cannot figure out if the approach can actually handle real environments.
%
%In my opinion, the paper deals with an interesting problem, but it also presents some questionable assumptions. Moreover, the experimental sections do not entirely prove the effectiveness of the proposed approach.

@@

@@

% {R ? R3×3 | RT R = I, det R = 1}
Consider a range sensor that provides scans of the surrounding environment in order to identify the closest occupied space. Let the measurement scan at the $t$-th time step be $Z_t$, where $z\in Z_t$ is a single measurement ray. Let the $t$-th pose be denoted by $X_t=\braces{x_t,R_t}$ with location $x_t\in\Re^3$ and attitude $R_t\in\SO=\braces{R\in\Re^{3\times3}|R^\T R=I,\det{R}=1}$, where $X_t$ is assumed to be known. Given the sensor probabilistic properties $p(z|X_t,m)$, commonly referred to as the \emph{forward sensor model}, the goal is finding the \emph{inverse sensor model}, $P(m|z,X_{1:t},Z_{1:t-1})$. To obtain this probability for all cells,~\cite{KauLeeAiMos16,KauTakAiLee17} introduced a reduced map $r\subset m$ composed of $n_r$ cells along $z$, where cells are indexed by increasing distance from $x_t$, and $\mathbf{r}_{k+}$ refers to the event that the $k$-th cell of map $r$ is the closest occupied space. Then, the inverse sensor model for the $k$-th cell is
\begin{align}
\label{eqn:RayISMAnswer}
P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1})&=\eta\tilde P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1}),
\end{align}
where the unnormalized probability of the inverse sensor model is defined as
\begin{align}
\label{eqn:Unnormalized}
\tilde P(\mathbf{r}_{k}|z,X_{1:t},&Z_{1:t-1})\nonumber\\
&=\mathbf{P}_k^-
\bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}\bar{\mathbf{P}}_j^-\bigg\}p(z|\mathbf{r}_{i+},X_t)\mathbf{P}_k^-\bigg]\nonumber\\
&\quad + \bigg\{\prod_{j=0}^{k-1}\bar{\mathbf{P}}_j^-\bigg\}p(z|\mathbf{r}_{k+},X_t)\mathbf{P}_k^-,
\end{align}
where a priori probability is $\mathbf{P}_k^-=P(\mathbf{r}_{k}|X_{1:t-1},Z_{1:t-1})$, its complement is $\bar{\mathbf{P}}_k^-=1-\mathbf{P}_k^-$, $P(\bar{\mathbf{r}}_{0}|X_{1:t-1},Z_{1:t-1})=P(\mathbf{r}_{n_r+1}|X_{1:t-1},Z_{1:t-1})=1$ for convenience, and $p(z|\mathbf{r}_{(n_r+1)+},X_t)$ represents the forward sensor model of a maximum sensor reading. The normalizer $\eta$ is given by
\begin{align}
\label{eqn:allEta}
\eta
&=
\bigg[\sum_{i=1}^{n_{r}+1}\bigg\{\prod_{j=0}^{i-1}\bar{\mathbf{P}}_j^-\bigg\} p(z|\mathbf{r}_{i+},X_t)\mathbf{P}_k^-\bigg]^{-1},
\end{align}
and it is independent of the cell index $k$. The proofs of \refeqn{RayISMAnswer}--\refeqn{allEta} are given in~\cite{KauLeeAiMos16}. Since the terms of \refeqn{Unnormalized} are easily obtained and several are used repeatedly to obtain \refeqn{allEta}, the computational cost of \refeqn{RayISMAnswer} is trivial and can be applied in real-time. This process is repeated for all measurements composing scan $Z_t$.

@@

The inverse sensor model from~\cite{KauLeeAiMos16,KauTakAiLee17} is based on an arbitrary vector spanning 2D space. The distances from the robot to grid cells are obtained geometrically through ray casting. This method is easily extended to 3D space, and the inverse sensor model is applied identically. Since the map is updated ray-by-ray (each measurement ray is considered once by itself), this approach is extended for measurement fusion of any number of sensors; the map is updated by each ray of a scan sequentially, then the map is updated by the rays of the next scan in queue, which might have different characteristics. There are several reasons why a robot might be equipped with multiple sensors, e.g., different fields-of-view or depth sensor properties. For example, a robot may be equipped with a 2D LIDAR with highly accurate measurements, but a limited single-plane field-of-view. Then, the robot can compensate for the LIDAR limitations with an IR depth sensor that provides many more measurement rays with a 3D scan, where each ray has lower accuracy than the LIDAR rays. Since each sensor model is explicitly considered in the cell probability calculations, measurements from both sensors may serve to update the same probabilistic map. However, the impact from a LIDAR measurement with high accuracy on the probabilistic map will be greater than that of the IR depth sensor with lower accuracy. Since sensor properties are considered explicitly, the proposed 3D mapping approach can fuse the impact of measurements on the probabilistic map from different sources with different properties.
% EditEK 1: example of 2 sensor measurements fused, starting with "For example, a robot may be equipped..." until the end of the paragraph.

However, implementation in 3D requires several careful considerations. First, the number of cell occupancy probabilities tracked with computer memory increases by a factor of the number of cells in the added dimension. In its current form, the proposed method assumes fixed map limits, so these should be carefully selected with grid cell resolution based on available memory. Second, measurement rays spanning 3D space typically involve more intersections with grid cells. The computational order of ray casting and the inverse sensor model are proportional to the number of grid cells along the ray $n_r$, so careful consideration must be placed on sensor limits and rays per scan that can be considered. Typically, computers small enough to be carried onboard flying robots lack the processing capabilities to update massive maps quickly, particularly because the ray-by-ray updating method requires many computations in series with large measurement scans. Therefore, an onboard computer can simply stream the sensor data, and a more powerful computer can run the mapping.
% EditEK 2: revised the sentence from:
% "Typically, computers small enough to be carried onboard flying robots lack the memory or processing capabilities to update massive maps quickly."
% to:
% Typically, computers small enough to be carried onboard flying robots lack the processing capabilities to update massive maps quickly, particularly because the ray-by-ray updating method requires many computations in series with large measurement scans.

Additionally, aerial vehicles are frequently subject to fast movements, and the time stamps for pose estimates and depth sensor readings are not guaranteed to align. For example, the most recent pose estimate and measurement scan may have significantly different time stamps while the robot is rapidly rotating. Using these together violates the assumption that the robot pose is well-known for every measurement scan, i.e., $X_t$ and $Z_t$ are given. Therefore, pose estimates and sensor readings must be paired according to their time stamps. A useful tool that easily satisfies this goal is the Message Filters package with the Robot Operating System (ROS), where stamped poses and measurement scans are synchronized using recently received data.
% EditEK 3: changed "message filtering" to "the Message Filters package"

@@

The goal of the proposed autonomous exploration strategy is moving to poses that maximize the information the robot expects to learn about the map, measured with entropy. To achieve this in real-time, careful consideration is placed on computational costs. In particular, the expected entropy computational order of a ray that intersects $n_r$ cells is $(n_r+1)^2$. Since most quadrotor flight is close to hover and floor plans exhibit little variation in the vertical direction, the proposed exploration uses 2D occupancy grid maps located at the desired exploration height. These assumptions correspond to rooms and hallways with non-complex geometries. This approach decreases $n_r$ and simplifies the exploration problem with 3D space. These 2D maps project important properties of the 3D map.
% Edit EK 4: Added the sentence: "These assumptions correspond to rooms and hallways with non-complex geometries."

@@

Gazebo is a 3D dynamic simulator~\cite{KaeHow04}, with plugins to simulate an Asus Xtion color depth sensor and a Hokuyo LIDAR. Gazebo also provides position and attitude transforms from the world to the quadrotor body, and the ability to set robot model states directly.

@@

There are two processes for exploration. The first process is projecting the 3D map onto 2D maps; the same code under different conditional parameters produces two nodes, for collision and entropy maps. The second process subscribes to these two 2D maps; the collision map serves as input for candidate pose consideration and Dijkstra's search, and the entropy map serves to predict information gain. This node provides path messages, composed of desired poses $0.01$sec apart, displayed with a ROS visualization package, Rviz.

@@

\begin{figure}[!t]
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_1min.jpg}
        		\caption{$t=1$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_2min.jpg}
        		\caption{$t=2$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_3min.jpg}
        		\caption{$t=3$min}
   	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_4min.jpg}
        		\caption{$t=4$min}
    	\end{subfigure}
	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_5min.jpg}
        		\caption{$t=5$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_6min.jpg}
        		\caption{$t=6$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_7min.jpg}
        		\caption{$t=7$min}
   	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_8min.jpg}
        		\caption{$t=8$min}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Simulated 3D Occupancy Grid Map}
\label{fig:sim3DMap}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.45\textwidth]{entropy_gazebo_aspect3by1.png}
	\caption{Simulated Environment Map Entropy}
	\label{fig:simH}
\end{figure}

@@

\section{Experimental Results}

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.95\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_north.jpg}
        		\caption{North Region}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.95\columnwidth}
	\vspace*{0.03\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_south.jpg}
        		\caption{South Region}
    	\end{subfigure}
	\caption{3D Experimental Environment}
	\label{fig:exp3DEnvironment}
\end{figure}

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.95\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_0min.jpg}
        		\caption{$0$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.95\columnwidth}
		\vspace*{0.03\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_1min.jpg}
        		\caption{$1$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.95\columnwidth}
	\vspace*{0.03\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min.jpg}
        		\caption{$2$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.95\columnwidth}
	\vspace*{0.03\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min47sec.jpg}
        		\caption{$2$min $47$sec (end)}
    	\end{subfigure}
	\caption{3D Occupancy Grid Map and Point Clouds}
	\label{fig:exp3DMap}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.45\textwidth]{entropy_experiment_aspect3by1.png}
	\caption{Experimental Environment Map Entropy}
	\label{fig:expH}
\end{figure}
